Scikit-learn: machine learning without learning the machinery

### 2014-07-01 article.tex
grammar + typo

\paragraph{Some history.}
%
Scikit-learn started circa 2007 as code from David Cournapeau and
Matthieu Brucher's PhD work, but dwindled down till 2010, year at which the
Parietal team from INRIA adopted the project, hiring a full time
engineer. Basics API were defined and an efficient binding of LibSVM
\cite{chang2011libsvm} gave the project a compelling advantage. In
December 2011, the first international sprint was organized with generous
funding from Google. Today, the project has grown vastly beyond
INRIA into a worldwide open source effort.

>>>>

\paragraph{Some history.}
%
Scikit-learn started circa 2007 as code from David Cournapeau and
Matthieu Brucher's PhD work, but dwindled down till 2010, in which year the
Parietal team from INRIA adopted the project, hiring a full time
engineer. Basic APIs were defined and an efficient binding of LibSVM
\cite{chang2011libsvm} gave the project a compelling advantage. In
December 2011, the first international sprint was organized with generous
funding from Google. Today, the project has grown vastly beyond
INRIA into a worldwide open source effort.
